What maketh a hit movie?
========================================================
I have movie data from 2014, mainly metadata. Questions this document will answer are:
* What is the distribution of incomes of the top earning actors?
* same income distribution for the directors?
* Which month releases did the best?
* Which movie genres make the most money?
* Do people like to watch long movies?

First, we will load our dataframes. 
We have two frames, one is the raw frame we got from scraping and joining data 
from boxofficemojo and rottentomatoes.
Second is the training data we created by cleaning the data in python.
```{r}
raw_frame = read.csv("raw_frame.csv", header=T,stringsAsFactors=F)
print("Columns in raw frame are:")
print(names(raw_frame))

clean_frame = read.csv("training_frame.csv", header=T, stringsAsFactors=F)
print("Columns in cleaned frame are:")
print(names(clean_frame))
```
Our first task would be to find how much has each of the top actors made?
There is some sleight of hand involved, since we saved these in the raw frame
as a python list which R does not quite recognize
```{r, echo=FALSE}
get_actor_vector = function(x)
{
  if(x=="")
    return( c())
  char_list = strsplit(x,',')[1]
  actor_names = c()
  for(char in char_list)
  {
    #remove special characters,leading, trailing spaces
    val = gsub('\\[|\\]|\\*|^\\s+|\\s+$|\'','',char)
    #replace spaces with _
    val = gsub('\\s+','_',val)
    actor_names = c(actor_names, val)
  }
  return(actor_names)
}

```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(cars)
```

